OpenMPIR

### 2017-09-07 paper.tex
Minor fixes

For other implementations, we compare to GCC 7.1, Clang 4.0.1, and Intel
17.0.0. The machine used is a two socket Intel Xeon E5-2683 v3 machine with
132GB of memory, running Linux 4.11.4. Each Xeon has 16 cores running at
2.1GHz, with 20M of L3 cache. All benchmarks were run using all 64
hyper-threads. 32 thread tests were run as a sanity check and showed
qualitatively similar results. It's worth noting that each of the other
implementations comes with it's own runtime. In this sense, performance is a
function of both the compiler and any optimizations it's able to perform, and
the runtime.  Understanding the interaction of these two parts is non-trivial,
as we will see when discussing results. Each compiler was run with the flags
\texttt{-O3 -fopenmp}. Our compiler was also run with \texttt{-ftapir} to
enable Tapir instructions.

@@

While we would like to distinguish between these, it is difficult to do so with
only performance counter information. A more thorough investigation would
require careful knowledge of each of the frontends and runtimes. One thing we
can guess at is that despite the focus of the paper, \emph{IR optimisations are
unlikely to be the cause of performance improvements}. Our evidence for this
comes from Shardl et al. \cite{tapir}. While some IR optimisations have been
implemented, they seem to have significantly more effect on parallel loop code,
while the tasking code remains relatively unaffected by IR optimizations
\cite{tapir}.

>>>>

For other implementations, we compare to GCC 7.1, Clang 4.0.1, and Intel
17.0.0. The machine used is a two socket Intel Xeon E5-2683 v3 machine with
132GB of memory, running Linux 4.11.4. Each Xeon has 16 cores running at
2.1GHz, with 20M of L3 cache. All benchmarks were run using all 64
hyper-threads. 32 thread tests were run as a sanity check and showed
qualitatively similar results. It's worth noting that each of the other
implementations comes with it's own runtime. In this sense, performance is a
function of both the compiler and any optimizations it's able to perform, and
the runtime.  Understanding the interaction of these two parts is non-trivial,
as we will see when discussing results. Each compiler was run with the flags
\texttt{-O3 -fopenmp}. Our compiler was also run with \texttt{-ftapir} to
enable Tapir instructions to be lowered to a parallel runtime (in this case,
the default Cilk runtime).

@@

While we would like to distinguish between these, it is difficult to do so with
only performance counter information. A more thorough investigation would
require careful knowledge of each of the frontends and runtimes. One thing we
can guess at is that despite the focus of the paper, \emph{IR optimisations are
unlikely to be the cause of performance improvements}. Our evidence for this
comes from Schardl et al. \cite{tapir}. While some IR optimisations have been
implemented, they seem to have significantly more effect on parallel loop code,
while the tasking code remains relatively unaffected by IR optimizations
\cite{tapir}.
